MSF_Groupwork-NBA_shotlog

### 2016-10-16 MSFGroupwork-NBAHotHand.Rmd
almost there!
last graph changes

** Table 9**: Relationship between the defender distance and accuracy

@@

```{r, echo=FALSE}
graph01 <- ggplot(special2) + geom_boxplot(aes(x = player_name, y = FGA, colour = W))
graph01 <- graph01 + labs(title = "Differences in FGA for games lost/won for particular players") + xlab("Player name") + ylab("FGA")
graph02 <- ggplot(special2) + geom_boxplot(aes(x = player_name, y = FG.percentage, colour = W)) 
graph02 <- graph02 + labs(title = "Differences in FG% for games lost/won for particular players") + xlab("Player name") + ylab("FG%")
grid.arrange(graph01, graph02, ncol = 2)
```

>>>>

**Table 9**: Relationship between the defender distance and accuracy

@@

```{r, echo=FALSE}
graph01 <- ggplot(special2) + geom_boxplot(aes(x = player_name, y = FGA, colour = W))+ graph01 + labs(title = "Differences in FGA for games lost/won for particular players") + xlab("Player name") + ylab("FGA")
graph02 <- ggplot(special2) + geom_boxplot(aes(x = player_name, y = FG.percentage, colour = W)) + labs(title = "Differences in FG% for games lost/won for particular players") + xlab("Player name") + ylab("FG%")
graph01
graph02
```
